Target Markdown

### 2022-09-02 _targets.Rmd
slightly changed pipeline to accomodate propensity score matching

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI"
                            ))

@@

     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path, nrows = 20),
              format = "qs"),
      tar_target(ids_complete, create_ids_complete(ids),
              format = "qs"),
    tar_target(ids_complete_vector,
               make_ids_complete_vector(ids_complete)),
    tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
    tar_target(all_pubs,
           get_all_pubs(db_path, ids_complete), 
              format = "qs"),
    tar_target(one_author,
           read_one_author(db_path, ids_complete_vector, ids_complete), 
              format = "qs", pattern = map(ids_complete_vector), iteration = "list")

>>>>

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt",
                            "plyr"
                            ))

@@

     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path, nrows = 20),
              format = "qs"),
      tar_target(ids_complete, create_ids_complete(ids),
              format = "qs"),
    tar_target(ids_complete_vector,
               make_ids_complete_vector(ids_complete)),
    tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite"))#,
    # tar_target(all_pubs,
    #        get_all_pubs(db_path, ids_complete), 
    #           format = "qs"),
    # tar_target(one_author,
    #        read_one_author(db_path, ids_complete_vector, ids_complete), 
    #           format = "qs", pattern = map(ids_complete_vector), iteration = "list")
    # 
)
```

# Matching and data preparation

```{targets matching_preparation}
list(

     tar_target(matching, match(db_path, ids)
                format = "qs"),
     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(all_pubs,
           get_all_pubs(db_path, matching, ids_complete), 
              format = "qs"),
    tar_target(one_author,
           read_one_author(db_path, ids_complete_vector, ids_complete), 
              format = "qs", pattern = map(ids_complete_vector), iteration = "list")
